Evaluation of clustering parameters - SCPCS000169

### 2024-08-02 analyses/cell-type-wilms-tumor-06/notebook/01-clustering_SCPCS000169.Rmd
change fetal kidney reference path

Note to the DataLab : where should I save the fetal kidney reference? In S3 like results as it is a quite big object or in the folder marker-sets?

For more information related to the reference, please go to https://www.kidneycellatlas.org/
You will find:

@@

# access to the azimuth kidney reference 
##### to be updated depending on the location of the reference file 
ref_dir = "~/mnt_resources/datasets/Kidney_cell_atlas/fetal_full/Azimuth_Compatible_Fetal_full"

>>>>

Note to the DataLab : where should I save the fetal kidney reference? 
In S3 like results as it is a quite big object or in the folder marker-sets?
The reference in now in the module folder, marker-sets
For more information related to the reference, please go to https://www.kidneycellatlas.org/

You will find:

@@

# access to the azimuth kidney reference 
##### to be updated depending on the location of the reference file 
ref_dir = file.path(module_base, "marker-sets/Azimuth_Compatible_Fetal_full/")
